Synthesizing Verified Components for Cyber Assured Systems Engineering \thanks{ Funded by DARPA Cyber Assured Systems Engineering (CASE) contract HR00111890001. }

### 2021-05-07 paper/system.tex
Add notes on core language normal form

\begin{figure}
  \[
    \begin{array}{rcl}
      \mathit{c}    & = & \konst{input}\ [(f : \tau)\ldots] \\
                    &   & \konst{output}\ [(f : \tau)\ldots] \\
                    &   & \konst{eq}\; [(f : \tau := \mathit{exp})\ldots] \\
                    &   & \konst{guarantee}\ [\mathit{bexp}\ldots]\\\\

@@

>>>>

\begin{figure}
  \[
    \begin{array}{rcl}
      \mathit{c}    & = & \konst{input}\ [(f : \tau)\ldots] \\
                    &   & \konst{output}\ [(f : \tau)\ldots] \\
                    &   & \konst{eq}\; [(f : \tau := \mathit{exp})\ldots] \\
                    &   & \konst{guarantee}\ [(\mathit{bexp})\ldots]\\\\

@@

Change the following paragraph and preceding paragraphs to define the specification as the core language with a well defined normal form where expressions are flat, lvals are unique etc. It takes care of all the normal semantic checks related to types, dependency order, etc. Anything in the core language has normal form and is perfect.
